### 2025-02-17 paper/paper.tex
Update text.

\subsubsection*{Training Process}
The agent is trained using a variant of the Advantage Actor-Critic (A2C) algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.

@@

The algorithm implements the A2C training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics. The actor network learns a policy that minimizes mistakes in predicting the true state, while the critic network estimates state values to compute advantages for policy updates.

@@

    \item \textit{Proportions of True Action}: The proportion of time each agent selects the correct action in their policy, reflecting how well the agents have learned to identify the optimal action.

>>>>

\subsubsection*{Training Process}
The agent is trained using a variant of the Advantage Actor-Critic algorithm. The complete training procedure is detailed in Algorithm \ref{alg:single-agent-training}.

@@

The algorithm implements the Advantage Actor Critic training loop, processing signals through GRU-based actor and critic networks while tracking learning metrics. The actor network learns a policy that minimizes mistakes in predicting the true state, while the critic network estimates state values to compute advantages for policy updates.

@@

    \item \textit{True Action Rates}: The proportion of how much the agent's mixed policy assings to the true action $a_\omega = 1$. This metric helps visualize the agent's learning progress.
